Draft

### 2023-04-18 Draft.Rmd
added reqs

---
title: "Draft"
author: "Aileen Li"
date: "2023-04-18"
output: html_document
---

@@

```{r}
library(tidyverse)
dat <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")

@@

>>>>

---
title: "Draft"
author: "Aileen Li"
date: "2023-04-18"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

Title and Introduction
Write a narrative introduction containing:
A description of the modeling approaches you have chosen for your comparison;
An explanation of how the predictor variables were chosen for your model;
Any exploratory analysis that was done with the data (e.g. correlations, scatterplots, boxplots, histograms, etc.) in order to learn about relationships in the data;
Your expectation for what the RMSE performance of your model should be.

```{r}
library(tidyverse)
origin <- read_csv("https://github.com/rdpeng/stat322E_public/raw/main/data/pm25_data.csv.gz")

@@

Wrangling
This section should include any wrangling or transformations of the data that were done prior to modeling. Code should be included throughout and 
a textual explanation should be included to explain any wrangling operations.

Results
Describe the development of your 3 prediction models (or 4 models, if working in a group) and
how you compared their performance. 
Be sure to describe the splitting of training and testing datasets 
and the use of cross-validation to evaluate prediction metrics. 
Remember that the primary metric for your prediction model will be root-mean-squared error (RMSE). 
Your results should include 
at least one visualization demonstrating the prediction performance of your models. 
You should also include 
a table summarizing the prediction metrics (including RMSE) across all of the models that you tried.

Discussion
Putting it all together, what did you learn from your data and your model performance?
• Answer your Question posed above, citing any supporting statistics, visualizations, or results from the data or your models.
• Reflect on the process of conducting this project. What was challenging, what have you learned from the process itself?
• Reflect on the performance of your final prediction model. Did it perform as well as you originally expected? If not, why do you think it didn’t perform as well?
• Include acknowledgments for any help received. If a group project, report the contribution of each member (i.e. who did what?).

Formatting
Create the report using R Markdown, with 
headers for each section; 
include comments to the R code; 
include references (datasets, context). 
The final report should be no more than 20 pages (the number of pages can vary greatly depending on the cleaning process).
It is extremely important that you select pages when submitting on Gradescope.
